\textbf{Empirical demonstration.} We retrained the FedAvg-default model under server-side fixed-clipping DP \cite{bonawitz2017practical, dwork2006differential} at four privacy budgets $\varepsilon \in \{1, 3, 10, \infty\}$ with $\delta=10^{-5}$ and three seeds per budget; noise multipliers were calibrated via Opacus's RDP accountant \cite{opacus2021}. Figure~\ref{fig:dp} shows the result. From the no-DP baseline to $\varepsilon=1$, pooled AUC degrades by $36\%$ ($0.81 \to 0.52$) while worst-site AUC degrades by $47\%$ ($0.73 \to 0.39$, with one seed below $0.23$ --- worse than random at Site~2). The 11-percentage-point gap is the empirical content of the \S VI claim that privacy mechanisms have a non-uniform shape of interaction with validity: tight DP budgets concentrate accuracy harm on the smallest, already-most-fragile site.

The calibration story is more severe still. Worst-site calibration slope deviation $|1 - \text{slope}|$ moves monotonically from $0.49$ at no-DP to $1.11$ at $\varepsilon=1$. A deviation of $1.0$ corresponds to a slope of zero, meaning the model has lost all discriminative signal at that site and outputs an essentially constant probability regardless of input. At $\varepsilon=1$, Site~2's calibration slope across the three seeds is $-0.186$, $-0.140$, and $+0.0001$ --- the model is no longer doing prediction, it is outputting a number. Importantly, Site~2 (Long Beach VA, $n_{\text{test}}{=}16$) is the worst site on calibration intercept in every one of the 12 runs across all four privacy budgets: DP does not shift \emph{which} site bears the burden, it amplifies the burden on the same site that was already most fragile at the no-DP baseline. A federation that publishes only the pooled AUC under DP can therefore advertise an apparently-acceptable global model that is clinically unusable at exactly the sites whose participation makes the federation valuable in the first place.

% Add to bibliography:
% \bibitem{opacus2021}
% A. Yousefpour \emph{et al.}, ``Opacus: User-friendly differential privacy library in PyTorch,'' arXiv:2109.12298, 2021.
